\begin{thebibliography}{99}

\bibitem{benton} Benton et. al. ``OpenFlow Vulnerability Assessment'' \emph{ACM SIGCOMM Hot Topics in Software Defined Networking (HotSDN)}, 2013. 

\bibitem{ethane} Casado et. al. ``Ethane: Taking Control of the Enterprise'' \emph{ACM SIGCOMM}, 2007.

\bibitem{sane} Casado et. al. ``SANE: A Protection Architecture for Enterprise Networks'' \emph{USENIX Security Symposium}, 2006.

\bibitem{cisco} Cisco. ``Multiple Vulnerabilities in Cisco TelePresence Multipoint Switch'' 11 July 2012 \url{tools.cisco.com/security/center/content/CiscoSecurityAdvisory/cisco-sa-20120711-ctms}

\bibitem{ciscopatch} Constantin, Lucian. ``Cisco patches vulnerabilities in some security applications, switches, and routers.'' \emph{InfoWorld} 10 October 2013, \url{http://www.infoworld.com/d/security/cisco-patches-vulnerabilities-in-some-security-appliances-switches-and-routers-228551}

\bibitem{dpkt} dugsong et. al. ``dpkt'' \url{code.google.com/p/dpkt}

\bibitem{history} Feamster et. al. ``An Intellectual History of Programmable Networks.'' \emph{ACM Queue} 2013.

\bibitem{muscular} Gellman et. al. ``How we know the NSA had access to internal Google and Yahoo cloud data'' \emph{Washington Post, The Switch}, 4 November 2013, \url{http://www.washingtonpost.com/blogs/the-switch/wp/2013/11/04/how-we-know-the-nsa-had-access-to-internal-google-and-yahoo-cloud-data/}

\bibitem{nox} Gude et. al. ``NOX: Towards an operating system for networks'' \emph{ACM SIGCOMM Computing Communication Review}, 2008.

\bibitem{hecker} Hecker, Artur. ``Carrier SDN: Security and Resilience Requirements'' 15 November 2013 \url{http://www.ikr.uni-stuttgart.de/Content/itg/fg524/Meetings/2013-11-15-Muenchen/12_ITG524_Muenchen_Hecker.pdf}

\bibitem{onix} Koponen et. al. ``Onix: a distributed control platform for large-scale production networks.'' \emph{USENIX Symposium on Operating Systems Design and Implementation (OSDI)}, 2010.

\bibitem{sdnsec} Kreutz et. al. ``Towards Secure and Dependable Software-Defined Networks'' \emph{ACM SIGCOMM HotSDN}, 2013.

\bibitem{openflow} McKeown et. al. ``OpenFlow: Enabling innovation in campus networks'' \emph{ACM SIGCOMM Computer Communication Review}, 2008.

\bibitem{resonance} Nayak et. al. ``Resonance: dynamic access control in enterprise networks'' \emph{ACM Workshop on Research on Enterprise Networking}, 2009.

\bibitem{opendaylight} Open Daylight, 2013-2014. \url{http://www.opendaylight.org}

\bibitem{protocol} ``OpenFlow Packet Protocol.'' \emph{OpenFlow}, \url{archive.openflow.org/wk/images/c/c5/Openflow_packet_format.pdf}

\bibitem{openvswitch} Pfaff et. al. ``Extending Networking into the Virtualization Layer'' \emph{ACM Workshop on Hot Topics in Networks (HotNets)}, 2009.

\bibitem{pox} POX developers. \url{http://www.noxrepo.org/pox/about-pox}

\bibitem{pycap} Rowe, Mark. ``Python Packet Capture and Injection Library'' \url{pycap.sourceforge.net}

\bibitem{ryu} ``Ryu SDN framework'' \url{http://osrg.github.io/ryu}

\bibitem{attacking} Shin and Gu. ``Attacking Software-Defined Networks: A First Feasibility Study'' \emph{ACM SIGCOMM HotSDN}, 2013.

\bibitem{tcqack} Stretch, Jeremy. ``Understanding TCP Sequence and Acknowledgement Numbers'' 7 June 2010, \url{http://packetlife.net/blog/2010/jun/7/understanding-tcp-sequence-acknowledgment-numbers/}

\end{thebibliography}
