\documentclass[12pt, letterpaper, twoside]{article}
%\usepackage{epstopdf}
%\usepackage[pdftex]{graphicx}
\usepackage[left=.8in,top=.8in,right=.8in,bottom=.8in,nohead,nofoot,columnsep=20pt]{geometry}
\usepackage{setspace}
\usepackage[small,compact]{titlesec}
\usepackage{subfigure}
\usepackage{multicol}
%\usepackage{multirow}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage[hyphens]{url}
\usepackage{float}
\usepackage{fancyhdr}
\setlength{\headheight}{14.5pt}
\setlength{\footskip}{11pt}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\rfoot{}

\title{Title goes in report.tex}
\author{Bonnie Eisenman, Michael Kranch and Anna Kornfeld Simpson}
\date{COS 597E Software Defined Networks \\ 14 January 2014}

\begin{document}

\maketitle

\begin{spacing}{1.0}

\begin{abstract}
This paper looks at the security concerns and potential vulnerabilities in Software Definined Networking (SDN). In particular, we examine additional attack vector of remotely introducing a switch into the networking path, something not possible without physical access to the switching site in a traditional network. We also look at the increased risk to the entire network from a single, compromised risk due to the centralized nature of SDN . We first provide an overview of SDN, the current status of security in SDN controllers, and discuss the threat models for our attack. We then introduce our roque switch and present several  attacks on various controller. We also discuss additional attacks possible by a rogue switch and examine additional vulnerabilities to a SDN from a single compromised switch. Finally, we conclude with some recommendations for hardening SDN controllers and limiting the area of attack.
\end{abstract}

\begin{multicols}{2}

\section{Introduction}
Paragraph about SDN - the various meanings of SDN and that we are discussing the traditional controller switch networking.

Not sure of difference between intro / background.

Things to discuss
-- Controllers
----Various Controller. That we are doing testing on Ryu and Pox (possibly OpenDaylight but its more complicated)
----Switches - In this context, a switch means either an OpenFlow capable hardware switch or a completely software defined switch (OpenVSwitch)

In section 2, we will.... In Section 3, etc. In Section 4, etc. Finally

We probably want to introduce things, right now that's in report.tex.  We might want to cite something in the introduction, we can do that using \begin{verbatim}{\cite{refname}\end{verbatim} where the \emph{refname} is defined in bibliography.tex in the \begin{verbatim}{\bibitem}\end{verbatim} command.  For example citing dpkt looks like this: \cite{dpkt}.

\section{Background}

\subsection{Software Defined Networking}

\subsection{Security in SDN}

\section{Creating a Software Defined Switch}

\subsection{OpenFlow Protocol}

\subsection{Initiating a Connection to a Controller}

\subsection{Push verses Pull Connections}

\label{fake}
I'm making up sections and order... there's a file called fake.tex where we can write about faking a switch. The verbatim environment is useful for preformatted text - there's an example in the introduction!
\input{fake}

\section{Disrupting an SDN with a Fake Switch}
\label{attacks}
There's a file called attacks.tex for describing our various attacks; we could combine the results of the attacks we implemented here, or put them separately.
\input{attacks}

\section{Related Work}
\label{related}
The related work might be long, so let's put it in a separate file, related.tex
\input{related}

\section{Conclusion}
The conclusion might be short enough to be in report.tex - we can add other sections before it as necessary, and the bibliography (in bibliography.tex) will follow.


% Imports the bibliography, don't remove
\input{bibliography}

\end{multicols}

\end{spacing}

\end{document}
